\newline
\section{Integration and Logistics}
\label{sec:Logistics}

\hspace*{0.5cm}
\begin{minipage}{\linewidth-0.5cm}
  \begin{enumerate}[label = \Alph*.]
    
  \item Date and Time of your arrival for integration: Planned arrival for integration is on July 23rd, 08:00 CT
    
  \item Approximate amount of time required for integration: integration will take no more than 1 hour.
    
  \item Name of the integration team leader: Samuel A. Garcia Morelos
    
  \item Email address of the integration team leader: samuel.morelos@gmail.com

  \item List ALL integration participants (first and last names) who will be present for integration with their email addresses: \newline
        Andrew Renshaw - arenshaw@centraluh.edu \newline
        Samuel A. Garcia Morelos - samuel.morelos@gmail.com \newline
        Fre’Etta Brooks - orgonzaa@gmail.com \newline
        Andrew Walker - andrewg.walker96@gmail.com \newline
        Kevin Portillo - kportillo01@gmail.com \newline
        Steven Oliver - oliversteven23@gmail.com \newline
        Jimish Patel- Jimishpatel75@gmail.com \newline

  \item A successful integration of the SORA payload will include the following: \newline
        A mechanical integration of the fully functioning SORA payload with the HASP platform. The payload will downlink the appropriate data to the HASP platform and ground station and maintain operations during the thermal vacuum testing. After meeting all HASP requirements, the SORA payload will remain 100\% functional.

        Our results for bacteria collection rely heavily on a very little to no contamination risk setting pre and post flight, therefore we think it best that the sampling system remain powered down until float altitude has been reached. Instead we can assemble a proxy for the integration testing in the form of a separate actuator and pump just to confirm that commands are being received from the ground. Once everything is determined to be in perfect working order the entire system will be shut down in preparation for the actual flight.

  \item List all expected integration steps:
        \begin{enumerate}[label = -]
          \item Mechanical System:
          \begin{enumerate}
            \item Ensure SORA properly fits and successfully attaches to the HASP platform.
            \item Weight of the payload passes verification test.
          \end{enumerate}
        \end{enumerate}

        \begin{enumerate}[label = -]
          \item Electrical System:
          \begin{enumerate}
            \item Successful power up, check all health status lights power on.
            \item Appropriate current draw from each sub-system and the system as a whole.
          \end{enumerate}
        \end{enumerate}

  \end{enumerate}
\end{minipage}



\hspace*{0.5cm}
\begin{minipage}{\linewidth-0.5cm}
  \begin{enumerate}[label = \Alph*]
    \setcounter{enumi}{7}
      
        \begin{enumerate}[label = -]
          \item Communications System:
          \begin{enumerate}
            \item Successful communication with and downlink to the HASP platform.
            \item Appropriate data storage (do a self-check and verify data collection rate).
          \end{enumerate}
        \end{enumerate}

        \begin{enumerate}[label = -]
          \item Environmental System Check:
          \begin{enumerate}
            \item Thermal and vacuum tests completed successfully for each system.
            \item Do a system health check.
          \end{enumerate}
        \end{enumerate}

  \item List all checks that will determine a successful integration:
        The successful completion of all procedures and checks from F and G define a successful integration.

  \item List any additional LSU personnel support needed for a successful integration other than directly related to the HASP integration (i.e. lifting, moving equipment, hotel information/arrangements, any special delivery needs…): None

  \item List any LSU supplied equipment that may be needed for a successful integration: None

  \item All dimensions drawings and circuit diagrams updated above.
    
  \end{enumerate}
\end{minipage}
