\newpage
\section{Integration and Logistics}
\label{sec:Logistics}

\hspace*{0.5cm}
\begin{minipage}{\linewidth-0.5cm}
  \begin{enumerate}[label = \Alph*.]
  \item Date and Time of your arrival for integration: \newline
    The UH integration team will arrive in Palestine, Texas on July 14th and arrive at NASA facilities on July 15th at 8:00 CT.
  \item Approximate amount of time required for integration: \newline
    Integration will take about an hour.
  \item Name of the integration team leader: \newline
    Reed Bronson Masek    
  \item Email address of the integration team leader: \newline
    r.masek97@gmail.com
  \item List ALL integration participants (first and last names) who will be present for integration with their email addresses: \newline
    Andrew Renshaw - arenshaw@centraluh.edu \newline
    Reed Masek - r.masek97@gmail.com \newline
    Aaron Boggs - aboggs100@yahoo.com \newline
    Abraham Vega - vegaabe21@gmail.com \newline
    Alex Carpy - alejandrocarpy@gmail.com \newline
    Aliasgar Kalavadwala - alikalavadwala@gmail.com \newline
    Augusto Rubio - augusthernandez@outlook.com \newline
    Carlos Amaya - carlos.amaya.texas@gmail.com \newline
    Carson Bush - cjb2015@live.com \newline
    Daniel Howard - dwhoward9109@live.com \newline
    Emily Humble - erhumble@gmail.com \newline
    Fre'Ette Brooks - orgonzaa@gmail.com \newline
    Huy Trong - huyquoctruong12345@gmail.com \newline
    Jimish Patel - jimbopatel57@gmail.com \newline
    Jose Alvarado - ja78688@gmail.com \newline
    Josephine Arguello - jarguello37@gmail.com \newline
    Kevin Fleming - kevin-fleming@sbcglobal.net \newline
    Khoa Ngo - khoangotran@gmail.com \newline
    Nicolas Castillo - nicolas@castillovargas.com \newline
    Sydney Ngiang - sydneyngiang@gmail.com \newline
    Taylor Hill - tdhill92@gmail.com \newline    
  \end{enumerate}
\end{minipage}
\newpage
\begin{minipage}{\linewidth-0.5cm}
  \begin{enumerate}[label = \Alph*.] \setcounter{enumi}{5}
  \item A successful integration of the SORA 3 payload will include the following: \newline
    The payload can successfully communicate will HASP systems which includes sending/receiving commands and downlinking data packets. A successful thermal vacuum test of the payload will ensure that the payload and its components remains fully powered (within the HASP limits) at all times, the astrobiology system is able to deploy and retract autonomously in response to changes in pressure, and the data recorded and received by the payload's instruments are accurate. Since the membrane filters used in our astrobiology system are expensive, we will not use any filters during integration.    
  \item List all expected integration steps:
    \begin{enumerate}[label = -]
    \item Mechanical:
      \begin{enumerate}
      \item Ensure that the payload is securely fastened to the HASP gondola.
      \item Confirm that the astrobiology system properly deploys and retracts.
      \end{enumerate}
    \item Electrical:
      \begin{enumerate}
      \item The overall amperage draw of the payload remains within the \SI{2.5}{\ampere} limit throughout the entire test.
      \item Confirm that each subsystem receives the appropriate amount of power for operation.
      \item The electrical properties of the organic solar cells are properly recorded.
      \end{enumerate}
    \item Communications:
      \begin{enumerate}
      \item The payload can properly receive and process commands sent from HASP.
      \item The payload can send corruption-free data packets to HASP.
        % \item Appropriate data storage (do a self-check and verify data collection rate.
      \end{enumerate}
    \end{enumerate}
  \item List all checks that will determine a successful integration:
    If all items listed in sections F. and G., Integration will have been successful.
  \item List any additional LSU personnel support needed for a successful integration other than directly related to the HASP integration (i.e. lifting, moving equipment, hotel information/arrangements, any special delivery needs…): \newline
    None.
  \item List any LSU supplied equipment that may be needed for a successful integration: \newline
    None.
  \end{enumerate}
\end{minipage}
